TGI-spinal-power

### 2022-04-28 analysis/tgispine_lme_power.Rmd
starting with simple model

>>>>

# Getting data frame and paths
```{r}
datPath <- '/Users/au706616/Documents/Experiments/SPINALTGI/'
setwd(datPath)

df_phs <- read.csv(file.choose())
```

Create the first model. There is one model for each rating (instead of using rating as a parameter in the model).
First, going to try this on a very simple model where effect of manipulation (TGI vs. control) will be tested on rating of cold thermode, with subject as random effect
```{r}
# Summarise data per rating, per participant
# although summary not needed!
sum_pain <- aggregate(VASburning~ID*manipulation*condition*cold_probe, median, data = df_phs)
sum_warm <- aggregate(VASwarm~ID*manipulation*condition*cold_probe, median, data = df_phs)
sum_cold <- aggregate(VAScold~ID*manipulation*condition*cold_probe, median, data = df_phs)

# first try this on just one, simple model. The effect of manipulation on cold rating, with ID as a random effect
model.cold <- glmer(VAScold ~ manipulation + (1|ID), family = 'poisson', data = df_phs)

```
